\documentclass[10pt]{article}
\parindent 0pt

\usepackage{mathpazo}
\usepackage{etaremune}
\usepackage{nopageno}
\usepackage{amsmath,amstext,color}
\usepackage[margin=1.0in]{geometry}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{fancyhdr}
\usepackage{hyperref}

\fancyhead[C]{Gillen Brown --- Resume}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot{}
\pagestyle{fancy}

\newcommand{\header}[1]{\vspace{1.5em}\par \textbf{\large #1}\strut\hrule\vspace{0em}}
%par makes it always go to the next line, strut produces slight vertical offset
% for the rule.

\newcommand{\actionHeader}[2]{\textbf{#1 \hfill #2}}
\newcommand{\indentedItemDate}[2]{\newline\null\qquad #1 \hfill #2}
\newcommand{\indentedItem}[1]{\newline\null\qquad #1}
% null lets the indents work after the space. Newlines allows me to have less
% whitespace in the Latex file.

\title{Gillen Brown}

\begin{document}
\thispagestyle{empty}

\setlist[itemize]{noitemsep, topsep=0pt}

\begin{center}
{\huge \bf Gillen Brown}

{\Large gillenbrown@gmail.com \enspace \rule[-5pt]{1pt}{20pt} \enspace \href{http://www.github.com/gillenbrown}{github.com/gillenbrown}}

\bigskip

\parbox[c][2em][s]{0.8\textwidth}{\center \large Future Ph.D graduate with extensive technical and analytic skills, seeking position in data science or computer science.}

\medskip

\end{center}

\header{Education}
\actionHeader{University of Michigan}{Ann Arbor, MI}
\indentedItemDate{Ph.D. in Astronomy}{September 2016-{\it May 2022}}
\indentedItem{{\bf Topic:} Chemical Evolution of Simulated Milky Way Sized Galaxies}
\indentedItem{{\bf Summary:} Added funtionality to existing C codebase that models galaxy formation, then ran }
\indentedItem{simulations on supercomputers such as NASA's Pleiades cluster to understand how different elements}
\indentedItem{are distributed within galaxies.}

\actionHeader{University of Missouri-Kansas City}{Kansas City, MO}
\indentedItemDate{B.S. Physics with emphasis in Astronomy}{May 2016}
\indentedItem{Math minor}
\indentedItem{Computer Science minor}
\indentedItem{4.0 GPA}

\header{Technical Skills}
\actionHeader{Extensive Experience}{}
\vspace{-0.6em}
\begin{itemize}
    \item Python (and associated scientific computing packages such as NumPy, SciPy, Matplotlib, Jupyter)
    \item C/C++
    \item Unix
    \item LaTeX
\end{itemize}

{\bf Some Experience} | R, HTML, CSS, git, Job Schedulers (Slurm, Torque)

\header{Soft Skills}
\begin{itemize}
    \item {\bf Technical/Scientific Writing} | Currently an author on three scientific articles, with more upcoming.
    \item {\bf Teaching} | Facilitated astronomy labs, designed and taught my own course, and will soon obtain a {\it Graduate Teaching Certificate} from the UM Center of Research on Learning and Teaching. 
    \item {\bf Collaboration} | Worked with several faculty and fellow graduate students on my thesis project.
    \item {\bf Public Speaking} | Presented my scientific work at conferences and other formal venues and more casual settings such as Ann Arbor Nerd Nite and Astronomy on Tap.
    \item {\bf Leadership} | Took leadership role among UM-Astronomy graduate students, including representing graduate students in several departmental settings.
    \item {\bf Critical Thinking} | Developed the ability to evaluate claims from myself and others in both qualitative and quantitative ways, including familiarity with statistical analyses
    \item {\bf Project Management} | Developed and executed thesis project spanning multiple years. 
    \item {\bf Problem Solving} | Discovered solutions to complex problems on the bleeding edge of scientific research on all levels of a project, from fixing technical glitches to developing creative experiments
\end{itemize}

\header{Awards}
\begin{itemize}
    \item {\bf Michigan Basketball Data Madness Challenge} --- Won a UM competition by extracting actionable insights from basketball player performance data.
\end{itemize}

\end{document}